Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recoginiton

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
fix typo
fix bracket
Few words about using speech-related information

The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
suggesting that BERT's extensive pre-training does provide some useful information for recoginizing different dialogue acts (Table~\ref{table:exp2}).
This performance boost is much more pronounced in the macro-averaged F1 score,
which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
For a disaggregeated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl} p

@@

@@

\bibliography{acl2020}
\bibliographystyle{acl_natbib}
\clearpage
\appendix

\begin{figure*}[h!]
\section{Supplementary materials}\label{sec:suppl}
  \centering
  \includegraphics[width=\linewidth]{img/SWDA-bertLvsNL.pdf}
  \includegraphics[width=\linewidth]{img/AMI-DA-bertLvsNL.pdf}
  \caption{Change in accuracy for each dialogue act (\texttt{BERT-NL} vs \texttt{BERT-L}). Positive changes when adding laughter (\texttt{BERT-L}) are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter. Top chart: SWDA, Bottom chart: AMI-DA. }
    \label{fig:by-da}
  \end{figure*}

\begin{figure*}[h!]
  \centering
  \includegraphics[width=\linewidth]{img/swda-brf.pdf}
  \includegraphics[width=\linewidth]{img/ami-brf.pdf}
  \caption{F1 scores by dialogue act for BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}). Dialogue acts are ordered with the most common on the left.
    \label{fig:f1-by-da}
  \end{figure*}

>>>>

The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
suggesting that BERT's extensive pre-training does provide some useful information for recoginizing different dialogue acts (Table~\ref{table:exp2}).
This performance boost is much more pronounced in the macro-averaged F1 score,
which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
For a disaggregeated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl}.

@@

There is abundant room for further progress in determining how other speech-related information, such as prosody and disfluencies, can be incorporated into the DAR model.
\citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve dialogue act classification.
Furthermore, function of laughter and its position in relation to laughable can be reflected in the acoustic form of laughter \citep{tian2016we,mazzocconi2019phd}.

@@

\bibliography{acl2020}
\bibliographystyle{acl_natbib}
\appendix
\onecolumn
\section{Supplementary materials}\label{sec:suppl}

\begin{figure*}[h!]
  \centering
  \includegraphics[width=\linewidth]{img/SWDA-bertLvsNL.pdf}
  \includegraphics[width=\linewidth]{img/AMI-DA-bertLvsNL.pdf}
  \caption{Change in accuracy for each dialogue act (\texttt{BERT-NL} vs \texttt{BERT-L}). Positive changes when adding laughter (\texttt{BERT-L}) are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter. Top chart: SWDA, Bottom chart: AMI-DA. }
    \label{fig:by-da}
  \end{figure*}

\begin{figure*}[h!]
  \centering
  \includegraphics[width=\linewidth]{img/swda-brf.pdf}
  \includegraphics[width=\linewidth]{img/ami-brf.pdf}
  \caption{F1 scores by dialogue act for BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}). Dialogue acts are ordered with the most common on the left.}
    \label{fig:f1-by-da}
  \end{figure*}
